Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-02-15 manuscript.tex
Update manuscript

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m.
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
The standard moment of inertia of the dumbbell model is 
\begin{align}\label{eq:dumbbell_moment_of_inertia}
    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
\end{align}
where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
\begin{align}\label{eq:sphere_moment_of_inertia}
    J_i = \begin{bmatrix} 
        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
        0 & \frac{2}{5} m_i r_i^2 & 0 \\
        0 & 0 & \frac{2}{5} m_i r_i^2 
    \end{bmatrix}.
\end{align}
\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
\begin{subequations}\label{eq:moi_transformation}
    \begin{align}
        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
    \end{align}
\end{subequations}     
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.

@@

The control gains are chosen based on the desired closed-loop system response. 
A variety of techniques are available to choose these gains, but a simple linear analysis offers a straightforward and systematic approach to choosing suitable values. 
We use the control inputs defined in~\cref{eq:translational_control,eqn:adaptive_control} and substitute them into the dynamic equations of motion in~\cref{eq:inertial_position_dynamics,eq:inertial_velocity_dynamics,eq:inertial_attitude_dynamics,eq:inertial_angvel_dynamics}.
\todo{add description of control}

@@

\section*{Appendix}

\subsection*{Proof of Attitude Configuration Error}\label{proof:attitude_configuration_error}
To prove~\cref{item:prop_psi_psd}, we first seek to show that \( A(R_d) \) is a critical point by showing that the first derivative is zero at \( R_d \).
The infinitesimal variation of a rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta}.
\end{align*}
Using this, the variation of~\cref{eq:A} is taken with respect to \( R \) as
\begin{align*}
	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
\end{align*}
where we used~\cref{eqn:hat1} to achieve the simplified form.
\Cref{eq:dirDiff_A} also proves~\cref{item:prop_eRA}.
Evaluating~\cref{eq:dirDiff_A} at \( R = R_d \) demonstrates that \( R_d \) is a critical point of \( A \).
Next, the second derivative of \( A \) is computed as
\begin{align*}
    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee  \\
    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee\\
    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee  \\
    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
\end{align*}
where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
Evaluating the Hessian at \( R = R_d \)
\begin{align}\label{eq:A_hessian}
    \Hess(A)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} \parenth{\tr{G}I -  G} \eta 
\end{align}
shows that the Hessian is positive definite at \( R_d \) and therefore the critical point is a minimum for any variation \( \eta \) and proves~\cref{item:prop_A_psd}.

To prove~\cref{item:prop_A_critical_points} we must first determine the critical points of~\cref{eq:eRA}.
The derivations are originally presented in~\cite{bullo2004,chaturvedi2011a} and we present and expand on their original descriptions.
We define the relative attitude error as \( Q = R_d^T R \) and expand~\cref{eq:eRA} as
\begin{align*}
    e_{R_A} &= \frac{1}{2} \parenth{G Q - Q^T G} ^ \vee, \\
            &= \frac{1}{2} \parenth{%
            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
            \begin{bmatrix} q_{11} & q_{12} & q_{13} \\ q_{21} & q_{22} & q_{23} \\ q_{31} & q_{32} & q_{33}\end{bmatrix}
            -
            \begin{bmatrix} q_{11} & q_{21} & q_{31} \\ q_{12} & q_{22} & q_{32} \\ q_{13} & q_{23} & q_{33}\end{bmatrix}
            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
            }^\vee , \\
            &= \frac{1}{2} \begin{bmatrix} g_3 q_{32} - g_2 q_{23} \\ g_1 q_{13} - g_3 q_{31} \\ g_2 q_{21} - g_1 q_{12}\end{bmatrix}
\end{align*}
At a critical point, the following equations must be satisfied
\begin{subequations}\label{eq:erA_critical_conditons}
    \begin{align}
        g_3q_{32} &= g_2 q_{23}, \\
        g_1 q_{13} &= g_3 q_{31}, \\
        g_2 q_{21} &= g_1 q_{12}.
    \end{align}
\end{subequations}     
Using the conditions in~\cref{eq:erA_critical_conditons} the relative attitude error \( Q \) becomes
\begin{align}\label{eq:relative_attitude_error}
    Q = R_d^T R_e =
    \begin{bmatrix} 
        q_{11} & q_{12} & q_{13} \\ 
        \frac{g_1}{g_2} q_{12} & q_{22} & q_{23} \\
        \frac{g_1}{g_3} q_{13} & \frac{g_2}{g_3} q_{23} & q_{33}
    \end{bmatrix}
    \in \SO
\end{align}
Since, \( Q = R_d^T R \) is orthonormal the main diagonal of \( QQ^T \) is equal to \num{1} and each column of \( Q \) is unit length.
\begin{align*}
    Q Q^T &= I, \\
          &= \begin{bmatrix}
    Q_{11} & Q_{12} & Q_{13} \\ 
    Q_{21} & Q_{22} & Q_{23} \\ 
    Q_{31} & Q_{32} & Q_{33} 
\end{bmatrix}, 
\end{align*}
where
\begin{align*}
    Q_{11} &= q_{11}^2 + q_{12}^2 + q_{13}^2 ,\\
    Q_{12} &= q_{11}q_{12}\frac{g_1}{g_2} + q_{12}q_{22} + q_{13}q_{23} ,\\
    Q_{13} &= q_{11}q_{13}\frac{g_1}{g_3} + q_{12}q_{23}\frac{g_2}{g_3} + q_{13}q_{33},\\
    Q_{21} &= q_{11}q_{12}\frac{g_1}{g_2}  + q_{12}q_{22} + q_{23}q_{13} ,\\
    Q_{22} &= \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 ,\\
    Q_{23} &= \frac{g_1^2}{g_2g_3} q_{12}q_{13} + \frac{g_2}{g_3}q_{23}q_{22} + q_{23}q_{33},\\
    Q_{31} &= \frac{g_1}{g_3} q_{11}q_{13} + \frac{g_2}{g_3}q_{23}q_{12} + q_{33}q_{13},\\
    Q_{32} &= \frac{g_1^2}{g_3 g_2} q_{12}q_{13} + \frac{g_2}{g_3} q_{23}q_{22} + q_{33} q_{23},\\
    Q_{33} &= \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2.
\end{align*}
As a result the following \num{6} conditions must be satisfied when \( e_{R_A} = 0 \):
\begin{align}
    q_{11}^2 + q_{12}^2 + q_{13}^2 &= 1,\label{eq:orthogonal_1} \\
    \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 &= 1, \label{eq:orthogonal_2}\\
    \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2 &= 1, \label{eq:orthogonal_3}\\
    q_{11}^2 + \frac{g_1^2}{g_2^2}q_{12}^2 + \frac{g_1^2}{g_3^2}q_{13}^2 &= 1, \label{eq:unit_norm_1}\\
    q_{12} + q_{22}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 &= 1, \label{eq:unit_norm_2}\\
    q_{13}^2 + q_{23}^2 + q_{33}^2 &= 1.\label{eq:unit_norm_3}
\end{align}
We can further simplify these relationships by rewriting~\cref{eq:orthogonal_1,eq:orthogonal_2,eq:orthogonal_3} as
\begin{align}
    q_{11}^2 &= 1 - q_{12}^2 - q_{13}^2 , \\
    q_{22}^2 &= 1 - \frac{g_1^2}{g_2^2} q_{12}^2 - q_{23}^2, \\
    q_{33}^2 &= 1 - \frac{g_1^2}{g_3^2}q_{13}^2 - \frac{g_2^2}{g_3^2}q_{23}^2 
\end{align}
and substituting these relationships into~\cref{eq:unit_norm_1,eq:unit_norm_2,eq:unit_norm_3} to arrive at
\begin{subequations}\label{eq:era_critical_point_conditions}
\begin{align}
    \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \label{eq:era_condition_1}\\
    \parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}}q_{23}^2 &= 0 , \label{eq:era_condition_2}\\
    \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0.\label{eq:era_condition_3}
\end{align}
\end{subequations}     
The relationships in~\cref{eq:era_critical_point_conditions} are equivalent to the statement that \( e_{R_A} = 0 \) and must also be satisfied at each critical point.
Since each \( g_i \) is distinct and greater than zero, the solution to~\cref{eq:erA_critical_conditons}, or equivalently \( e_{R_A} = 0 \), must satisfy one of two possible conditions:
\begin{enumerate}[label=(\roman*)]
    \item \label{item:condition_1} \( q_{12} = q_{13} = q_{23} =0\)
    \item \label{item:condition_2} \( q_{ij} \neq 0 \; \forall \; i \neq j \)
\end{enumerate}
These conditions can be determined by noticing that~\cref{item:condition_1} is the trivial solution.
For~\cref{item:condition_2}, consider the situation that \( q_{12} \neq 0 \) then from the fact that \( g_i \) are distinct yields the fact that \( \parenth{1 - \frac{g_1^2}{g_2^2} } \neq 0 \) and \( \parenth{1 - \frac{g_1^2}{g_3^2} } \neq 0 \) which means that \( q_{13}^2 \neq 0 \) since the terms must add to zero.
Similar arguments can be made for the other relations in~\cref{eq:era_critical_point_conditions} which means that the solutions must satisfy either~\cref{item:condition_1} or~\cref{item:condition_2}.

Now consider~\cref{item:condition_2} and assume that \( g_2 > g_1 \) and \( q_{12}, q_{13}, q_{23} \neq 0 \).
From~\cref{eq:era_condition_1} this implies that \( \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 > 0\) since \( q_{12}^2 > 0\).
Therefore, in order for~\cref{eq:era_condition_1} to be satisfied means that \( \parenth{1 - \frac{g_1^2}{g_3^2} } q_{13}^2 < 0 \) which further implies that \( g_1 > g_3 \).
As a result, \( g_2 > g_1 > g_3 \).
Using this inequality in~\cref{eq:era_condition_3} implies that
\begin{align*}
    \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23} < 0, \quad \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 < 0.
\end{align*}
Therefore the left hand side of~\cref{eq:era_condition_3} is negative and a contradiction.
Applying a similar logic for the case \( g_1 > g_2 \) shows that~\cref{item:condition_2} is not possible and therefore~\cref{item:condition_1} must be satisfied.
Substituting~\cref{item:condition_1} into~\cref{eq:relative_attitude_error} shows that the main diagonal of \( Q \) must be composed of \( + 1 \) or \( -1 \).
Thus, the critical points of \( A(R) \) are those provided in~\cref{item:prop_A_critical_points}.
These critical points correspond to additional rotations of \SI{180}{\degree} about each axes, or more explicitly \( R_e = \braces{R_d, R_\alpha, R_\beta, R_\gamma} \) where
\begin{align}
    R_\alpha &= R_d \begin{bmatrix} 1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & -1 \end{bmatrix} , \\
    R_\beta &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & 1 \end{bmatrix} , \\
    R_\gamma &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & -1 \end{bmatrix}.
\end{align}

The original proof for~\cref{item:prop_psi_quadratic} is presented in~\cite{lee2011a} and summarized in this section.
Define \( Q = R_d^T R = \exp \hat{\vc{x}} \in \SO \) for any \( \vc{x} \in \R^3 \) from Rodrigues' formula
\begin{align}\label{eq:rodrigues_formula}
    Q = \exp{\theta \hat{\vc{x}}} = I + \sin \theta \vh{x} + \parenth{1 - \cos \theta} \vh{x}^2 \in \SO.
\end{align}
Using a symbolic computation tool one can then find
\begin{align}\label{eq:psi_rodrigues}
    A &= \frac{1 - \cos \norm \vc{x}}{2\norm{\vc{x}^2}} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j} x_k^2, \\
    \norm{e_{R_A}}^2 &= \frac{\parenth{1 - \cos \norm{\vc{x}}^2} }{4 \norm{\vc{x}}^4}  \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i - g_j}^2 x_i^2 x_j^2 + \frac{\sin^2 \norm{\vc{x}}}{4 \norm{\vc{x}}^2} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j}^2 x_k^2,
\end{align}
where \( \mathcal{C} = \braces{ \parenth{1, 2, 3} , \parenth{2, 3, 1} , \parenth{3, 1, 2} } \).
Using~\cref{eq:psi_rodrigues} one can show
\begin{align}
    \frac{\norm{e_{R_A}}^2}{A} \leq \frac{h_2 + h_3}{h_1} , \quad \frac{A}{\norm{e_{R_A}}^2} \leq \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi} } ,
\end{align}
which proves~\cref{item:prop_A_quadratic}.

>>>>

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \label{eq:x_dot}\\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \label{eq:R_dot}\\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m. \label{eq:omega_dot}
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
The standard moment of inertia of the dumbbell model is 
\begin{align}\label{eq:dumbbell_moment_of_inertia}
    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
\end{align}
where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
\begin{align}\label{eq:sphere_moment_of_inertia}
    J_i = \begin{bmatrix} 
        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
        0 & \frac{2}{5} m_i r_i^2 & 0 \\
        0 & 0 & \frac{2}{5} m_i r_i^2 
    \end{bmatrix}.
\end{align}
\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
\begin{subequations}\label{eq:moi_transformation}
    \begin{align}
        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
    \end{align}
\end{subequations}     
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.

@@

The control gains are chosen based on the desired closed-loop system response. 
A variety of techniques are available to choose these gains, but a simple linear analysis offers a straightforward and systematic approach to choosing suitable values. 
We use the control inputs defined in~\cref{eq:translational_control,eqn:nodist_control} and substitute them into the dynamic equations of motion in~\cref{eq:x_dot,eq:v_dot,eq:R_dot,eq:omega_dot}.

@@

%\section*{Appendix}

%\subsection*{Proof of Attitude Configuration Error}\label{proof:attitude_configuration_error}
%To prove~\cref{item:prop_psi_psd}, we first seek to show that \( A(R_d) \) is a critical point by showing that the first derivative is zero at \( R_d \).
%The infinitesimal variation of a rotation matrix is defined as
%\begin{align*}
%    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta}.
%\end{align*}
%Using this, the variation of~\cref{eq:A} is taken with respect to \( R \) as
%\begin{align*}
%	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
%%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
%\end{align*}
%where we used~\cref{eqn:hat1} to achieve the simplified form.
%\Cref{eq:dirDiff_A} also proves~\cref{item:prop_eRA}.
%Evaluating~\cref{eq:dirDiff_A} at \( R = R_d \) demonstrates that \( R_d \) is a critical point of \( A \).
%Next, the second derivative of \( A \) is computed as
%\begin{align*}
%    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee  \\
%    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee\\
%    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee  \\
%    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
%\end{align*}
%where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
%Evaluating the Hessian at \( R = R_d \)
%\begin{align}\label{eq:A_hessian}
%    \Hess(A)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} \parenth{\tr{G}I -  G} \eta 
%\end{align}
%shows that the Hessian is positive definite at \( R_d \) and therefore the critical point is a minimum for any variation \( \eta \) and proves~\cref{item:prop_A_psd}.

%To prove~\cref{item:prop_A_critical_points} we must first determine the critical points of~\cref{eq:eRA}.
%The derivations are originally presented in~\cite{bullo2004,chaturvedi2011a} and we present and expand on their original descriptions.
%We define the relative attitude error as \( Q = R_d^T R \) and expand~\cref{eq:eRA} as
%\begin{align*}
%    e_{R_A} &= \frac{1}{2} \parenth{G Q - Q^T G} ^ \vee, \\
%            &= \frac{1}{2} \parenth{%
%            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
%            \begin{bmatrix} q_{11} & q_{12} & q_{13} \\ q_{21} & q_{22} & q_{23} \\ q_{31} & q_{32} & q_{33}\end{bmatrix}
%            -
%            \begin{bmatrix} q_{11} & q_{21} & q_{31} \\ q_{12} & q_{22} & q_{32} \\ q_{13} & q_{23} & q_{33}\end{bmatrix}
%            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
%            }^\vee , \\
%            &= \frac{1}{2} \begin{bmatrix} g_3 q_{32} - g_2 q_{23} \\ g_1 q_{13} - g_3 q_{31} \\ g_2 q_{21} - g_1 q_{12}\end{bmatrix}
%\end{align*}
%At a critical point, the following equations must be satisfied
%\begin{subequations}\label{eq:erA_critical_conditons}
%    \begin{align}
%        g_3q_{32} &= g_2 q_{23}, \\
%        g_1 q_{13} &= g_3 q_{31}, \\
%        g_2 q_{21} &= g_1 q_{12}.
%    \end{align}
%\end{subequations}     
%Using the conditions in~\cref{eq:erA_critical_conditons} the relative attitude error \( Q \) becomes
%\begin{align}\label{eq:relative_attitude_error}
%    Q = R_d^T R_e =
%    \begin{bmatrix} 
%        q_{11} & q_{12} & q_{13} \\ 
%        \frac{g_1}{g_2} q_{12} & q_{22} & q_{23} \\
%        \frac{g_1}{g_3} q_{13} & \frac{g_2}{g_3} q_{23} & q_{33}
%    \end{bmatrix}
%    \in \SO
%\end{align}
%Since, \( Q = R_d^T R \) is orthonormal the main diagonal of \( QQ^T \) is equal to \num{1} and each column of \( Q \) is unit length.
%\begin{align*}
%    Q Q^T &= I, \\
%          &= \begin{bmatrix}
%    Q_{11} & Q_{12} & Q_{13} \\ 
%    Q_{21} & Q_{22} & Q_{23} \\ 
%    Q_{31} & Q_{32} & Q_{33} 
%\end{bmatrix}, 
%\end{align*}
%where
%\begin{align*}
%    Q_{11} &= q_{11}^2 + q_{12}^2 + q_{13}^2 ,\\
%    Q_{12} &= q_{11}q_{12}\frac{g_1}{g_2} + q_{12}q_{22} + q_{13}q_{23} ,\\
%    Q_{13} &= q_{11}q_{13}\frac{g_1}{g_3} + q_{12}q_{23}\frac{g_2}{g_3} + q_{13}q_{33},\\
%    Q_{21} &= q_{11}q_{12}\frac{g_1}{g_2}  + q_{12}q_{22} + q_{23}q_{13} ,\\
%    Q_{22} &= \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 ,\\
%    Q_{23} &= \frac{g_1^2}{g_2g_3} q_{12}q_{13} + \frac{g_2}{g_3}q_{23}q_{22} + q_{23}q_{33},\\
%    Q_{31} &= \frac{g_1}{g_3} q_{11}q_{13} + \frac{g_2}{g_3}q_{23}q_{12} + q_{33}q_{13},\\
%    Q_{32} &= \frac{g_1^2}{g_3 g_2} q_{12}q_{13} + \frac{g_2}{g_3} q_{23}q_{22} + q_{33} q_{23},\\
%    Q_{33} &= \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2.
%\end{align*}
%As a result the following \num{6} conditions must be satisfied when \( e_{R_A} = 0 \):
%\begin{align}
%    q_{11}^2 + q_{12}^2 + q_{13}^2 &= 1,\label{eq:orthogonal_1} \\
%    \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 &= 1, \label{eq:orthogonal_2}\\
%    \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2 &= 1, \label{eq:orthogonal_3}\\
%    q_{11}^2 + \frac{g_1^2}{g_2^2}q_{12}^2 + \frac{g_1^2}{g_3^2}q_{13}^2 &= 1, \label{eq:unit_norm_1}\\
%    q_{12} + q_{22}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 &= 1, \label{eq:unit_norm_2}\\
%    q_{13}^2 + q_{23}^2 + q_{33}^2 &= 1.\label{eq:unit_norm_3}
%\end{align}
%We can further simplify these relationships by rewriting~\cref{eq:orthogonal_1,eq:orthogonal_2,eq:orthogonal_3} as
%\begin{align}
%    q_{11}^2 &= 1 - q_{12}^2 - q_{13}^2 , \\
%    q_{22}^2 &= 1 - \frac{g_1^2}{g_2^2} q_{12}^2 - q_{23}^2, \\
%    q_{33}^2 &= 1 - \frac{g_1^2}{g_3^2}q_{13}^2 - \frac{g_2^2}{g_3^2}q_{23}^2 
%\end{align}
%and substituting these relationships into~\cref{eq:unit_norm_1,eq:unit_norm_2,eq:unit_norm_3} to arrive at
%\begin{subequations}\label{eq:era_critical_point_conditions}
%\begin{align}
%    \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \label{eq:era_condition_1}\\
%    \parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}}q_{23}^2 &= 0 , \label{eq:era_condition_2}\\
%    \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0.\label{eq:era_condition_3}
%\end{align}
%\end{subequations}     
%The relationships in~\cref{eq:era_critical_point_conditions} are equivalent to the statement that \( e_{R_A} = 0 \) and must also be satisfied at each critical point.
%Since each \( g_i \) is distinct and greater than zero, the solution to~\cref{eq:erA_critical_conditons}, or equivalently \( e_{R_A} = 0 \), must satisfy one of two possible conditions:
%\begin{enumerate}[label=(\roman*)]
%    \item \label{item:condition_1} \( q_{12} = q_{13} = q_{23} =0\)
%    \item \label{item:condition_2} \( q_{ij} \neq 0 \; \forall \; i \neq j \)
%\end{enumerate}
%These conditions can be determined by noticing that~\cref{item:condition_1} is the trivial solution.
%For~\cref{item:condition_2}, consider the situation that \( q_{12} \neq 0 \) then from the fact that \( g_i \) are distinct yields the fact that \( \parenth{1 - \frac{g_1^2}{g_2^2} } \neq 0 \) and \( \parenth{1 - \frac{g_1^2}{g_3^2} } \neq 0 \) which means that \( q_{13}^2 \neq 0 \) since the terms must add to zero.
%Similar arguments can be made for the other relations in~\cref{eq:era_critical_point_conditions} which means that the solutions must satisfy either~\cref{item:condition_1} or~\cref{item:condition_2}.

%Now consider~\cref{item:condition_2} and assume that \( g_2 > g_1 \) and \( q_{12}, q_{13}, q_{23} \neq 0 \).
%From~\cref{eq:era_condition_1} this implies that \( \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 > 0\) since \( q_{12}^2 > 0\).
%Therefore, in order for~\cref{eq:era_condition_1} to be satisfied means that \( \parenth{1 - \frac{g_1^2}{g_3^2} } q_{13}^2 < 0 \) which further implies that \( g_1 > g_3 \).
%As a result, \( g_2 > g_1 > g_3 \).
%Using this inequality in~\cref{eq:era_condition_3} implies that
%\begin{align*}
%    \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23} < 0, \quad \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 < 0.
%\end{align*}
%Therefore the left hand side of~\cref{eq:era_condition_3} is negative and a contradiction.
%Applying a similar logic for the case \( g_1 > g_2 \) shows that~\cref{item:condition_2} is not possible and therefore~\cref{item:condition_1} must be satisfied.
%Substituting~\cref{item:condition_1} into~\cref{eq:relative_attitude_error} shows that the main diagonal of \( Q \) must be composed of \( + 1 \) or \( -1 \).
%Thus, the critical points of \( A(R) \) are those provided in~\cref{item:prop_A_critical_points}.
%These critical points correspond to additional rotations of \SI{180}{\degree} about each axes, or more explicitly \( R_e = \braces{R_d, R_\alpha, R_\beta, R_\gamma} \) where
%\begin{align}
%    R_\alpha &= R_d \begin{bmatrix} 1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & -1 \end{bmatrix} , \\
%    R_\beta &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & 1 \end{bmatrix} , \\
%    R_\gamma &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & -1 \end{bmatrix}.
%\end{align}

%The original proof for~\cref{item:prop_psi_quadratic} is presented in~\cite{lee2011a} and summarized in this section.
%Define \( Q = R_d^T R = \exp \hat{\vc{x}} \in \SO \) for any \( \vc{x} \in \R^3 \) from Rodrigues' formula
%\begin{align}\label{eq:rodrigues_formula}
%    Q = \exp{\theta \hat{\vc{x}}} = I + \sin \theta \vh{x} + \parenth{1 - \cos \theta} \vh{x}^2 \in \SO.
%\end{align}
%Using a symbolic computation tool one can then find
%\begin{align}\label{eq:psi_rodrigues}
%    A &= \frac{1 - \cos \norm \vc{x}}{2\norm{\vc{x}^2}} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j} x_k^2, \\
%    \norm{e_{R_A}}^2 &= \frac{\parenth{1 - \cos \norm{\vc{x}}^2} }{4 \norm{\vc{x}}^4}  \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i - g_j}^2 x_i^2 x_j^2 + \frac{\sin^2 \norm{\vc{x}}}{4 \norm{\vc{x}}^2} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j}^2 x_k^2,
%\end{align}
%where \( \mathcal{C} = \braces{ \parenth{1, 2, 3} , \parenth{2, 3, 1} , \parenth{3, 1, 2} } \).
%Using~\cref{eq:psi_rodrigues} one can show
%\begin{align}
%    \frac{\norm{e_{R_A}}^2}{A} \leq \frac{h_2 + h_3}{h_1} , \quad \frac{A}{\norm{e_{R_A}}^2} \leq \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi} } ,
%\end{align}
%which proves~\cref{item:prop_A_quadratic}.
